Testing with Grein et al. data

### 2020-05-29 dev/hmm_grein.Rmd
Testing m4 with stable states

```{r}
m2_hidden_state_data <- m1_hidden_state_data

@@

>>>>

```{r}
m2_hidden_state_data <- rbind(
  tibble(base = disease_levels) %>% mutate(corresponding_obs = base) %>% 
    crossing(tibble(state_group = c("_improving","_worsening"))) %>% 
    mutate(id = factor(paste0(base, state_group))) %>%
    select(-base, -state_group),
  tibble(id = c("Death","Discharge")) %>% mutate(corresponding_obs = id)
)

@@

## Improving/worsening/stable

```{r}
m4_hidden_state_data <- rbind(
  tibble(base = disease_levels) %>% mutate(corresponding_obs = base) %>% 
    crossing(tibble(state_group = c("_improving", "_stable", "_worsening"))) %>% 
    mutate(id = factor(paste0(base, state_group))) %>%
    select(-base, -state_group),
  tibble(id = c("Death","Discharge")) %>% mutate(corresponding_obs = id)
)

m4_observed_state_data <- m1_observed_state_data

m4_rate_data <- rbind(
  tibble(.from = paste0(disease_levels, "_worsening"), .to = "Death", rate_group = "death"),
  tibble(.from = "AA_improving", .to = "Discharge", rate_group = "improve_one"),
  tibble(.from = paste0(disease_levels[2 : length(disease_levels)], "_improving"), 
             .to = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_improving"), 
             rate_group = "improve_one"),
  tibble(.from = paste0(disease_levels[1 : (length(disease_levels) - 1)],"_worsening"), 
             .to = paste0(disease_levels[2 : length(disease_levels)], "_worsening"), 
             rate_group = "worsen_one"),
  tibble(.from = paste0(disease_levels,"_stable"), 
             .to = paste0(disease_levels, "_improving"), 
             rate_group = "to_improving"),
  tibble(.from = paste0(disease_levels,"_stable"), 
             .to = paste0(disease_levels, "_worsening"), 
             rate_group = "to_worsening"),
  tibble(.from = paste0(disease_levels,"_worsening"), 
             .to = paste0(disease_levels, "_stable"), 
             rate_group = "worsening_to_stable"),
  tibble(.from = paste0(disease_levels,"_improving"), 
             .to = paste0(disease_levels, "_stable"), 
             rate_group = "improving_to_stable")
  ) %>%
  mutate(.rate_id = factor(1:n())) %>%
  recode_group("death") %>%
  recode_group("improve_one") %>%
  recode_group("worsen_one") %>%
  recode_group("to_improving") %>%
  recode_group("to_worsening") %>%
  recode_group("improving_to_stable") %>%
  recode_group("worsening_to_stable")

m4_initial_states <- series_data %>% filter(.time == 1) %>% arrange(.serie) %>% pull(.observed) %>% paste0(., "_worsening")

m4_prior = m1_prior

m4_formula <- update.formula(m2_formula,
  ~ . + is_improving_to_stable + is_worsening_to_stable + (0 + is_improving_to_stable | improving_to_stable_id) + 
    (0 + is_worsening_to_stable | worsening_to_stable_id))

m4 <- brmshmmdata(m4_formula, series_data, 
                  m4_rate_data, m4_hidden_state_data, m4_initial_states, prior = m4_prior,
                  observed_state_data = m1_observed_state_data)

m4_fit <- brmhmm(m4, cache_file = paste0(cache_dir,"/grein_m4.rds"), control = list(adapt_delta = 0.9))

summary(m4_fit$brmsfit)
```

```{r}
m4_epred_rect <- posterior_epred_rect(m4_fit)
m4_predicted_rect <- posterior_epred_to_predicted(m4_fit, m4_epred_rect)
m4_predicted <- posterior_rect_to_long(m4_fit, m4_predicted_rect)
```

```{r}
m4_predicted_df <- posterior_long_to_df(m4_fit$data, m4_predicted)

step_size <- 6
for(step in 1:ceiling(m4_fit$data_processed$standata$N_series / step_size)) {
  series_id <- ((step - 1) * step_size + 1) : (step* step_size)

  posterior_state_plot(m4_predicted_df, series_id, m4_fit$data) %>% print()

```{r}
pp_check_last_state(m4_fit, m4_predicted_rect)
pp_check_transitions_direction(m4_fit, m4_predicted_rect)
pp_check_transitions_direction(m4_fit, m4_predicted_rect, states_from = 2:7)
```

```{r}
pp_check_transitions(m4_fit, m4_predicted_rect, states_from = 2:4)
pp_check_transitions(m4_fit, m4_predicted_rect, states_from = 5:7)
